---
title: "R Notebook -- A Very Brief Introduction"
output: html_notebook
---



## A Very Brief Introduction

In this introductory tutorial, I will use the work from an exercise that I completed to show how R Notebook documents work.



## A Very Brief Chunk

Below is our first example of a "chunk". Chunks are used to execute R code within the document.

```{r code1}
Code <- "Some code goes here."

```



## Executing a Chunk

Now, let's execute a chunk! Because the above chunk includes no output, we will print "Code" in order to illustrate chunk output:

```{r code2}
Code <- "Some code goes here."
print(Code)

```


Chunks are not independent! That is, you can have a chunk further along in your R Notebook document work with a variable defined
    in an earlier chunk:

```{r code3}
print(Code)
```




## 

RStudio includes the 50x2 list "cars" as a default variable. We make use of that list here to show an example of a more
    visual output:
    
```{r code4}
plot(cars)
```




